A High-Level Embedded Language for Low-Level GPU Kernel Programming

### 2013-10-02 src2/hl/paperThesis.tex
apa

The CUDA code we need to write by hand is very simple and only describes the 
actual order of the kernels we wish to launch. We make no changes to the 
kernels themselves. The listing below shows an outline
of the CUDA code for launching {\tt red5l} to give $2^{24}$ (= 16777216)
element reduction.

%% The listing in appendix \ref{app:A} shows an outline
%% of the CUDA code for launching {\tt red5l} to give $2^{24}$ (= 16777216)
%% element reduction.   
%% \pagebreak

@@

  return SUCCESS; 
\end{Verbatim} 
\end{small}

>>>>

The CUDA code we need to write by hand is very simple and only describes the 
actual order of the kernels we wish to launch. We make no changes to the 
kernels themselves. The listing in figure~\ref{fig:cudareductioncode} shows an outline
of the CUDA code for launching {\tt red5l} to give $2^{24}$ (= 16777216)
element reduction.

%% The listing in appendix \ref{app:A} shows an outline
%% of the CUDA code for launching {\tt red5l} to give $2^{24}$ (= 16777216)
%% element reduction.   
%% \pagebreak
\begin{figure} 
\begin{small}
\begin{Verbatim}[samepage=true]

@@

  return SUCCESS; 
\end{Verbatim} 
\end{small}
\caption{CUDA code that combines reduction kernels into reduction of a large array.}
\label{fig:cudareductioncode}
\end{figure}
